Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-03-29 paper_jasa_abstract.tex
abstract added

\begin {abstract} 
Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis. Until recently there were no formal visual methods in place for determining statistical significance of findings. This changed, when \citet{buja:2009} conceptually introduced two protocols for formal tests of visual findings. In this paper we take this a step further by comparing the lineup protocol \citep{buja:2009} against classical statistical testing  of the significance of regression model parameters. A human subjects experiment is conducted using simulated data to provide controlled conditions. Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
\end {abstract}

>>>>

\begin {abstract} 
Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis. Until recently there were no formal visual methods in place for determining statistical significance of findings. This changed, when Buja et al. (2009) conceptually introduced two protocols for formal tests of visual findings. In this paper we take this a step further by comparing the lineup protocol (Buja et al., 2009) against classical statistical testing  of the significance of regression model parameters. A human subjects experiment is conducted using simulated data to provide controlled conditions. Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
\end {abstract}
